Artin Group Presentations Arising from Cluster Algebras

### 2015-08-21 journal-of-pure-and-applied-algebra-submission/journal-of-pure-and-applied-algebra-paper.tex
added hailees version

\documentclass[11pt]{amsart}

@@

\title{Artin Group Presentations Arising from Cluster Algebras}
\author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
\email{jhaley3@nd.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
\date{\today}
\keywords{Artin group, cluster algebra, diagram representations}

@@

\section{Acknowledgements}
\thanks{This work was supported by the RTG grant NSF/DMS-1148634. We would also like to thank the University of Minnesota School of Mathematics for hosting us. We are greatly appreciative of Gregg Musiker's mentoring, support, and guidance on this problem. We thank Emily Gunawan for her useful comments on our work. We also thank Vic Reiner for motivating this problem.}

>>>>

\documentclass[11pt]{elsarticle}

@@

\title{Artin Group Presentations Arising from Cluster Algebras}
\author{Jacob Haley \fnref{haley}}
\address{University of Notre Dame, Department of Mathematics\\
Notre Dame IN 46556}

\author{David Hemminger \fnref{hemminger}}
\address{Duke University, Mathematics Department \\
Box 90320, Durham NC 27708-0320}

\author{Aaron Landesman \fnref{landesman}}
\address{Harvard University, Department of Mathematics\\
One Oxford Street, Cambridge MA 02138}

\author{Hailee Peck \fnref{peck}}
\address{Millikin University, Department of Mathematics \\
1184 W Main St., Decatur IL 62522}
%\ead{jhaley3@nd.edu}
%\ead{david.hemminger@duke.edu}
%\ead{aaronlandesman@college.harvard.com}
%\ead{hpeck@millikin.edu}

\fntext[haley]{jachaley@umich.edu}
\fntext[hemminger]{dhemminger@math.ucla.edu}
\fntext[landesman]{aaronlandesman@college.harvard.com}
\fntext[peck]{hpeck@millikin.edu}

\date{\today}
\begin{keyword} Artin group \sep
cluster algebra \sep
diagram mutations
\end{keyword}

@@

\section{Acknowledgements}
This work was supported by the RTG grant NSF/DMS-1148634. We would also like to thank the University of Minnesota School of Mathematics for hosting us. We are greatly appreciative of Gregg Musiker's mentoring, support, and guidance on this problem. We thank Emily Gunawan for her useful comments on our work. We also thank Vic Reiner for motivating this problem.

\vspace{0.5cm}
